Technical comment on `Negative-assortative mating for color in wolves'

### 2022-08-29 ms/ms.Rmd
finalizing submission

# Data availability

The source code is available in a public GitHub repository (https://github.com/cdmuir/disassortative-mating) and is archived on Zenodo (https://doi.org/10.5281/zenodo.7003312).

@@

Kirk Lohmueller and two anonymous reviewers provided feedback and mathematical derviations that greatly improved this manuscript.

>>>>

# Data accessibility

The source code is available in a public GitHub repository (https://github.com/cdmuir/disassortative-mating) and is archived on Zenodo and Dryad.

@@

Kirk Lohmueller and two anonymous reviewers provided feedback and mathematical derivations that greatly improved this manuscript.

### 2022-08-29 ms/ms.tex
finalizing submission

The previous section showed that the frequency of assortative gray \(\times\) black matings was not derived in a manner logically consistent with the model's assumptions. Here I derive new mating frequencies, genotype frequencies, and equilibria. This model was previously analyzed by Li (\protect\hyperlink{ref-li_first_1976}{1976}){]} where in his notation \(D = H + Q\), \(R = P\), and \(w = A\) (\emph{cf} pg. 367-368). I used Sympy version 1.8 (\protect\hyperlink{ref-meurer_sympy:_2017}{Meurer et al. 2017}) for symbolic derivations through Python version 3.6 and the \emph{R} package \textbf{reticulate} version 1.25 (\protect\hyperlink{ref-ushey_reticulate_2022}{Ushey et al. 2022}). All other computations were performed in \emph{R} version 4.2.0 (\protect\hyperlink{ref-r_core_team_r_2022}{R Core Team 2022}).

@@

\hypertarget{data-availability}{%
\section{Data availability}\label{data-availability}}

The source code is available in a public GitHub repository (\url{https://github.com/cdmuir/disassortative-mating}) and is archived on Zenodo (\url{https://doi.org/10.5281/zenodo.7003312}).

>>>>

The previous section showed that the frequency of assortative gray \(\times\) black matings was not derived in a manner logically consistent with the model's assumptions. Here I derive new mating frequencies, genotype frequencies, and equilibria. This model was previously analyzed by Li (\protect\hyperlink{ref-li_first_1976}{1976}){]} where in his notation \(D = H + Q\), \(R = P\), and \(w = A\) (\emph{cf} pg. 367-368). I used Sympy version 1.7.1 (\protect\hyperlink{ref-meurer_sympy:_2017}{Meurer et al. 2017}) for symbolic derivations through Python version 3.6 and the \emph{R} package \textbf{reticulate} version 1.25 (\protect\hyperlink{ref-ushey_reticulate_2022}{Ushey et al. 2022}). All other computations were performed in \emph{R} version 4.2.1 (\protect\hyperlink{ref-r_core_team_r_2022}{R Core Team 2022}).

@@

\hypertarget{data-accessibility}{%
\section{Data accessibility}\label{data-accessibility}}

The source code is available in a public GitHub repository (\url{https://github.com/cdmuir/disassortative-mating}) and is archived on Zenodo and Dryad.
